\documentclass[11pt]{article}

\usepackage[
  left=0.65in,
  right=0.65in,
  top=0.4in,
  bottom=0.3in
]{geometry}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage[none]{hyphenat}
\usepackage[T1]{fontenc}
\usepackage{sourcesanspro}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}
  {\bfseries\fontsize{12.5pt}{14pt}\selectfont}
  {}{0em}{}
\titlespacing*{\section}{0pt}{4pt}{2pt}
\setlist[itemize]{
  noitemsep,
  parsep=0pt,
  topsep=0pt,
  leftmargin=1.2em,
  rightmargin=2em
}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}
\raggedbottom

\begin{document}

\begin{center}
    {\LARGE \textbf{Jerome Siljan}} \\
    JeromeSiljan@gmail.com \;|\; (469) 733-8585 \;|\; \href{https://github.com/JeromeSiljanUTA}{GitHub}
\end{center}

\vspace{3pt}

\section*{Summary}
Software Engineer with experience building scalable backend systems and full-stack applications in financial services, specializing in cloud infrastructure, event-driven architectures, and geospatial data platforms.

\vspace{3pt}

\section*{Technical Skills}
\textbf{Languages:} C\#, Python, JavaScript (Node.js, React.js), Go, SQL

\textbf{Tools/Libraries:} Azure, Terraform, .NET, FastAPI, NoSQL, Microsoft SQL Server, Docker, Linux

\vspace{3pt}

\section*{Work Experience}

\textbf{General Motors Financial – Software Development Engineer} \hfill Mar 2025 -- Present
\begin{itemize}
    \item Built and deployed backend services supporting AML business verification workflows for GM Financial Canada, processing 300k+ applications annually in production.
    \item Designed and implemented RESTful APIs and Azure Functions using Cosmos DB to power scalable, event-driven workflows and asynchronous processing.
    \item Owned provisioning of QA infrastructure using Terraform, establishing infrastructure-as-code practices that improved environment consistency and deployment reliability.
    \item Diagnosed and resolved performance and reliability issues in Azure-based systems, improving application stability and operational efficiency.
    \item Supported onboarding of new engineers by documenting system architecture and guiding debugging and development workflows.
\end{itemize}

\textbf{RapidEdge Analytics – Founding Engineer (Part-time)} \hfill Apr 2025 -- Feb 2026
\begin{itemize}
    \item Architected and deployed a full-stack geospatial analytics platform using React, FastAPI, and Go, enabling dynamic, map-based data exploration.
    \item Designed and implemented backend services integrating external APIs (U.S. Census Bureau, TomTom) to support real-time geospatial data enrichment.
    \item Built asynchronous processing and caching layers to efficiently handle large geospatial datasets and reduce data retrieval latency.
    \item Deployed and maintained a production environment using Docker, Supabase (Postgres), and Cloudflare, configuring container networking, routing, and security.
    \item Led end-to-end system design, including API architecture, data modeling, and infrastructure setup for a production-ready application.
\end{itemize}

\textbf{Photon – Full Stack Developer (Consultant)} \hfill Oct 2024 -- Mar 2025
\begin{itemize}
    \item Designed and built an LLM-driven pipeline to generate Gherkin test scenarios from Java source code, reducing manual test case creation effort.
    \item Parsed and chunked code using AST-based analysis, storing embeddings in Milvus and implementing a RAG pipeline for accurate, context-aware generation.
    \item Delivered prototypes and technical recommendations that informed client decisions on adopting AI-driven testing solutions.
\end{itemize}

\textbf{Buxtonco – Data Analyst} \hfill Jun 2024 -- Oct 2024
\begin{itemize}
    \item Developed analytics solutions using consumer and geospatial data to support site selection and marketing strategies, generating insights that informed store placement and customer targeting.
    \item Delivered client-facing analyses and recommendations adopted by companies including BioLife and Red Wing Shoes to guide location planning, marketing campaigns, and engagement strategies.
\end{itemize}

\textbf{Citigroup – PBWMT Summer Analyst} \hfill Jun 2023 -- Aug 2023
\begin{itemize}
    \item Developed and automated a data integration pipeline using Impala and AutoSys to process 20k+ records daily into HDFS, improving data ingestion reliability and efficiency.
    \item Contributed to the development of a document scanning and OCR application, streamlining the credit card application process and reducing manual data entry.
\end{itemize}

\vspace{3pt}

\section*{Education}
Bachelor of Science in Computer Engineering, The University of Texas at Arlington

\end{document}
